
\chapter*{Acknowledgements}
\begin{SingleSpace}


\initial{T}his work would not exist without the support of a great many people. I would first like to thank John Russo and Paddy Royall, without whom this project would not exist. Their advice and support has been foundational to my journey from student to scientist, and has remained a constant despite their departures from Bristol. I would also like to thank Tanniemola Liverpool and Henkjan Gersen, who adopted me late into my project and gave the advice and encouragement I needed to get this work over the line.

I consider myself incredibly fortunate to have undertaken my PhD through the BCFN. No one could wish for a warmer welcome than I received from the community cultivated by Annela Seddon and Ian Lindsey. The word \textit{family} has often been used internally to describe the BCFN and it is a sentiment I share enthusiastically. I began my studies through the BCFN in 2017 with a cohort of wonderful people, we have all undergone this journey together and I'm immensely proud of all of you. 

This work was predominantly conducted in the company of the students and postdocs who make up the Royall group. In many ways this work stands upon the small day to day interactions taking place in the lab, the office, or the pub. I have become very fond of you all, and I would especially like to thank Abraham, Yushi, Katherine, Nariaki, Josh, Francesco and Ioatzin, for many helpful discussions that have been essential to my getting here. I would also like to thank Claire Noble, as the other half of the "Biochemistry thesis club" it has been my pleasure to write in your company.

For me, as is the case with many people, I have found that there is an intangible part to a PhD that leaves the university and settles into the corner of whichever room one finds themselves in.
In regard to this aspect I would like to give thanks to a number of people outside of academia who have made this work possible: the various inhabitants and associates of 15d Beaufort road, especially Sam Hueget, Sam Smithers, Will Dixon and Peter Rosso, who's real and imaginary parts have performed great feats of heroism over these past years. Teo Garcia Millan, and many others who have helped me to climb to new heights. Flynn, who is cute and fluffy. My parents, who are my greatest champions. Their love and support have made innumerable contributions, \newline I love you both. Finally, Rachel, you have been here through all of the highs and lows, for the nights when reaching this moment seemed impossible, and popping prosecco at calls for eureka. I am forever grateful for your support. I love you.     



\end{SingleSpace}
\clearpage